---
title: "Assignment 3"
output: html_document
---

### Predict annual restaurant sales based on objective measurements

With tons of restaurants across the globe this business happens to be one of the most 
popular businesses ever. Restaurants employ millions of people in all countries and make 
significant daily investments in developing new restaurant sites. Right now, deciding 
when and where to open new restaurants is largely a subjective process based on the 
personal judgement and experience of development teams. This subjective data is difficult 
to accurately extrapolate across geographies and cultures. New restaurant sites take 
large investments of time and capital to get up and running. When the wrong location for 
a restaurant brand is chosen, the site closes within 18 months and operating losses are 
incurred. Finding a mathematical model to increase the effectiveness of investments in new restaurant 
sites would allow employers to invest more in other important business areas, like 
sustainability, innovation, and training for new employees. Using demographic, real estate, 
and commercial data, this competition challenges you to predict the annual restaurant sales 
of 100,000 regional locations. 

### Description of data

TFI is the company behind some of the world's most well-known 
brands: Burger King, Sbarro, Popeyes, Usta Donerci, and Arby’s.
TFI has provided a dataset with 137 restaurants in the training 
set, and a test set of 100000 restaurants. The data columns include 
the open date, location, city type, and three categories of obfuscated data: 
Demographic data, Real estate data, and Commercial data. The revenue column 
indicates a (transformed) revenue of the restaurant in a given year and is 
the target of predictive analysis. 

### Data fields

* Id : Restaurant id. 
* Open Date : opening date for a restaurant
* City : City that the restaurant is in. Note that there are unicode in the names. 
* City Group: Type of the city. Big cities, or Other. 
* Type: Type of the restaurant. FC: Food Court, IL: Inline, DT: Drive Thru, MB: Mobile
* P1, P2 - P37: There are three categories of these obfuscated data. Demographic data 
are gathered from third party providers with GIS systems. These include population in 
any given area, age and gender distribution, development scales. Real estate data mainly 
relate to the m2 of the location, front facade of the location, car park availability. 
Commercial data mainly include the existence of points of interest including schools, 
banks, other QSR operators.
* Revenue: The revenue column indicates a (transformed) revenue of the restaurant in a 
given year and is the target of predictive analysis. Please note that the values are 
transformed so they don't mean real dollar values. 

```{r}
# plotly is part of ropensci
library(plotly)
set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]
p <- ggplot(data = d, aes(x = carat, y = price)) + 
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)
(gg <- ggplotly(p))
```

You can also embed plots, for example:

```{r, echo=FALSE}

```


